The human in the loop: volunteer-based metacomputers as a socio-technical system

### 2016-04-24 Alife16/paper.tex
Cut a bit on the paragraph refs f731441

JavaScript can be used for either unwitting
\citep{unwitting-ec,boldrin2007distributed} or volunteer 
\citep{langdon:2005:metas,gecco07:workshop:dcor} distributed
evolutionary computation and it has been used ever since by several
authors, including more recent efforts
\citep{Desell:2008:AHG:1389095.1389273,duda2013distributed,DBLP:journals/corr/abs-0801-1210}. Many other researchers have
%Pablo: Desell in 2008 is not so recent
used Java \citep{chong:1999:jDGPi} and others have gone away from the
server-based paradigm to embrace peer to peer systems
\citep{jin2006constructing,10.1109/ICICSE.2008.99,DBLP:conf/3pgcic/GuervosMFEL12}. These computing
platforms to avoid single points of failure (the server) but, since they
need a certain amount of infrastructure installed in the client, the
threshold to join them is much lower; but once the infrastructure of P2P systems is in place
the gathering of new users becomes 
immediate and spontaneous, so that they can be used for short
algorithms on call.

>>>>

JavaScript can be used for either unwitting
\citep{unwitting-ec,boldrin2007distributed} or volunteer
\citep{langdon:2005:metas,gecco07:workshop:dcor} distributed
evolutionary computation and it has been used ever since by several
authors, including more recent efforts
\citep{Desell:2008:AHG:1389095.1389273,duda2013distributed,DBLP:journals/corr/abs-0801-1210}. Many
other researchers have used Java \citep{chong:1999:jDGPi}; others have
embraced peer to peer systems
\citep{jin2006constructing,10.1109/ICICSE.2008.99,DBLP:conf/3pgcic/GuervosMFEL12}. These
computing platforms avoid single points of failure (the server) and
once installed need no effort to gather new users for an experiment,
but the cost of acquiring new users is high since they need to be set
up.
